Towards a classification framework for social machines

### 2013-02-26 latex/paper_new.tex
intermediary version

The paper presents the current version of the framework. We envision a reiteration of the main clusters and constructs based on discussions with and feedback from various scientific audiences. We provide initial evidence of the usefulness of the framework as a tool to  examine commonalities and differences between social machines in Section \ref{sec:usage}, in which we applied the repertory grid elicitation technique to a set of $20$ social machines instances ranked by popularity according to the Alexa service.\footnote{\url{www.alexa.com/}} A more thorough evaluation will

>>>>

The paper presents the current version of the framework. We envision a reiteration of the main clusters and constructs based on discussions with and feedback from various scientific audiences. We provide initial evidence of the usefulness of the framework as a tool to  examine commonalities and differences between social machines in Section \ref{sec:usage}, in which we applied the repertory grid elicitation technique to a set of $20$ social machines instances ranked by popularity according to the Alexa service.\footnote{\url{www.alexa.com/}} A more thorough evaluation will assess the extent to which the classification constructs identified can be meaningfully used to
